---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- Add a project state badge
See https://github.com/BCDevExchange/Our-Project-Docs/blob/master/discussion/projectstates.md
If you have bcgovr installed and you use RStudio, click the 'Insert BCDevex Badge' Addin. -->

# bandaidr

Description of package
_Initiated: Nov. 8, 2019 at the BC gov R-hackathon in Prince George_

### Features

1. Read in Satellite data
  - needs a function to get the data
2. Name and Store the names of the bands (e.g. RGB, nIR, swir(?))
  - add names
  - satellites supported
  - look-up table of the bands
3. Provide information about the bands.  This could be vignette-popups with a short description and links to further information.

[Sentinel Bands (10m) ](https://sentinel.esa.int/image/image_gallery?uuid=c5fa6c3e-2978-4fb8-ac95-3be9c5171be2&groupId=247904&t=1345630320883)

### Resources for Group
_resources and items to consider_

- Various Satelites programs and the various the products that are available -- _need to clarify the scope of sat. programs supported_. 

#### LandSat Products


- LANDSAT_ETM_C1 
- LANDSAT_MSS_C1
- LANDSAT_TM_C1
- LANDSAT_8_C1


#### Naming Convensions

- [Sentinel Naming Convensions](https://sentinel.esa.int/web/sentinel/user-guides/sentinel-2-msi/naming-convention)
- [Landsat Naming Convensions](https://www.usgs.gov/faqs/what-naming-convention-landsat-collections-level-1-scenes?qt-news_science_products=0#qt-news_science_products)




### Accounts needed
- [USGS Landsat Registration](https://ers.cr.usgs.gov/register/)
  - this covers MODIS and Landsat data
- [Sentinel](https://scihub.copernicus.eu/dhus/)






### Installation
_NOT yet_


### Usage

#### Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### Project Status

Initiated


### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/bandaidr/issues/).

### How to Contribute

If you would like to contribute to the package, please see our
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2019 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.*
